

\beginsong{Elvis Costello - Radio Radio}

\gtab{A}{X02220}
\gtab{A/C#}{X42220}
\gtab{A/E}{0X2220}
\gtab{B}{X24442}
\gtab{B/D#}{XX1402}
\gtab{B/F#}{2:0X2220}
\gtab{B7}{X21202}
\gtab{C#m}{X42120}
\gtab{E}{022100}

\beginverse
{\nolyrics Intro: \[E] \[B7] \[E] \[B] (x2)}
\endverse

\beginverse
I was \[E]tuning in the shine on the \[B]light night dial
Doing \[A]anything my radio advised\[E].
With \[E]every one of those \[B]late night stations
Playing \[A]songs, bringing tears to my eyes.\[C#m]
I was \[A]seriously thinking about \[B]hiding the receiver
When the \[A/C#]switch broke 'cause it's old\[B/D#].
\[A/E]They're saying things that I can \[B/F#]hardly believe.
They really \[B]think we're getting out of con\[E]trol.
\endverse

\beginchorus
\[E]Radio is the \[C#m]sound salvation.
Radio is \[B]cleaning up the nation.
They \[A]say you better \[E]listen to the \[B]voice of \[E]reason.
But they don't \[A]give you any \[E]choice 'cause they \[B]think that it's \[C#m]treason.
So you had \[B]better do as you are told. \[C#m]
You better \[B]listen to the radio. \[E]
\endchorus

\beginverse
{\nolyrics \[E] \[B7] \[E] \[B] (x2)}
\endverse

\beginverse
\[Am]I want to bite the \[E]hand that feeds me.
\[Am]I want to bite \[E]that hand so badly.
\[C#m]I want to make them wish they'd never \[B7]seen me.
\endverse

\beginverse
\[E]Some of my friends sit a\[B]round every evening
And they \[A]worry about the times a\[E]head.
But \[E]everybody else is over\[B]whelmed by indifference
And the \[A]promise of an early \[E]bed.
You better \[A]shut up or get cut up;
They don't \[B]wanna hear about it.
It's only \[A/C#]inches on the reel-to-reel\[B/D#].
And the \[A/E]radio is in the hands of \[B/F#]such a lot of fools
Trying to a\[B]naesthetise the way that you \[E]feel.
\endverse

\beginverse
[Chorus]
\endverse

\beginverse
{\nolyrics \[E] \[B7] \[E] \[B] (x2)}
\endverse

\beginverse
Wonderful \[E]radio \[B7] \[E] \[B]
Marvelous \[E]radio \[B7] \[E] \[B]
Wonderful \[E]radio \[B7] \[E] \[B]
Radio, \[E]radio. \[B7] \[E] \[B]
Radio, \[E]radio. \[B7] \[E] \[B]
\endverse

\endsong


