

\beginsong{Mary Poppins - Chim Chim Cheree}

\gtab{Cm}{XX1013}
\gtab{Cm7}{XX1313}
\gtab{D7-5}{XX0112}
\gtab{F}{133211}
\gtab{Fm}{XX3111}
\gtab{G+}{XX1003}
\gtab{G7+}{XX1001}

\beginverse
{\nolyrics Intro: \[Cm] \[G7/9] \[Cm6] \[G7] \[Cm] \[G7-9] \[Cm6] \[G7]}
\endverse

\beginverse
\[Cm]Chim chiminey, \[G+]chim chiminey, \[Cm7]chim chim che\[F]ree! 
A \[Fm]sweep is as \[Cm]lucky, as \[D]lucky \[D7-5]can \[G7]be. 
\[Cm]Chim chiminey, \[G+]chim chiminey, \[Cm7]chim chim che\[F]roo! 
Good \[Fm]luck will rub \[Cm]off when I \[G7]shake \[G7+]'ands with \[Cm]you, 
Or \[Fm]blow me a \[Cm]kiss and \[G7]that's lucky \[Cm]too.
\endverse

\beginverse
\[Cm]Now as the \[G+]ladder of \[Cm7]life 'as been \[F]strung, 
you \[Fm]may think a \[Cm]sweep's on the \[D]bottom \[D7-5]most \[G7]rung. 
Though \[Cm]I spends me \[G+]time in the \[Cm7]ashes and \[F]smoke, 
in \[Fm]this 'ole wide \[Cm]world there's no \[G7]happier\[G+] \[Cm]bloke.
\endverse

\beginverse
\[Cm]Up where the \[G+]smoke is all \[Cm7]billered and \[F]curled, 
'Tween \[Fm]pavement and \[Cm]stars, 
is the \[D]chimney \[D7-5]sweep \[G7]world. \[G+]
\[G7]When there's \[Cm]'ardly no \[G+]day nor \[Cm7]hardly no \[F]night, 
there's \[Fm]things'alf in \[Cm]shadow and \[G7]'alfway\[C+] \[G7]in light\[Cm], 
On the \[Fm]rooftops of \[Cm]London, \[G7]coo, what a \[Cm]sight!
\endverse

\beginchorus
\[Cm]Chim chiminey, \[G+]chim chiminey, \[Cm7]chim chim che\[F]ree! 
When \[Fm]you're with a \[Cm]sweep you're in \[D]glad \[D7-5]compa\[G7]ny. 
\[Cm]Nowhere is \[G+]there a more \[Cm7]'appier \[F]crew 
Than \[Fm]them what sings "\[Cm]chim chim che\[G7]ree, \[C+]chim \[G7]cheroo\[Cm]!"
Chim \[Fm]chiminey \[Cm]chim chim, \[G7]cheree chim chee\[Cm]roo!
\endchorus

\beginverse
\[Cm]I choose me \[G+]bristles with \[Cm7]pride, yes, I \[F]do: 
A \[Fm]broom for the \[Cm]shaft and a \[D]brush \[D7-5]for the \[G7]flue.
\[Cm]Tough I'm covered with \[G+]soot from the \[Cm7]'ead to me \[F]toes,
A \[Fm]sweep knows 'es \[Cm]welcome wher\[D]ever \[D7-5]he \[G7]goes.
\endverse

\beginverse
\[Cm]Up where the \[G+]smoke is all \[Cm7]billered and \[F]curled, 
'Tween \[Fm]pavement and \[Cm]stars, 
is the \[D]chimney \[D7-5]sweep \[G7]world. \[G+]
\[G7]When there's \[Cm]'ardly no \[G+]day nor \[Cm7]hardly no \[F]night, 
there's \[Fm]things'alf in \[Cm]shadow and \[G7]'alfway\[C+] \[G7]in light\[Cm], 
On the \[Fm]rooftops of \[Cm]London, \[G7]coo, what a \[Cm]sight!
\endverse

\beginverse
[Chorus]
\endverse
\endsong
