

\beginsong{Michael Jackson - Billie Jean}

\gtab{F#m}{244222}
\gtab{Bm}{224442}
\gtab{D}{XX0232}
\gtab{C#}{4:002220}

\beginverse
\endverse

\beginverse
{\nolyrics Intro: \[F#m]}
\endverse

\beginverse
\[F#m]She was more like a beauty queen from a movie scene
I said don`t mind but what do you mean, I am the \[Bm]one  
Who will dance on the floor in the \[F#m]round
She said I am the \[Bm]one
Who will dance on the floor in the round? \[F#m]
\endverse

\beginverse
\[F#m]She told me her name was Billie Jean as she caused a scene.
Then ev`ry head turned with eyes that dreamed \[Bm]of being the one,
Who will dance on the floor in the \[F#m]round
\endverse

\beginverse
\[D]People always told me, be \[F#m]careful what you do.
\[D]And don`t go around breaking young girls' \[F#m]hearts
And \[D]mother always told me, be \[F#m]careful who you love,
And be \[D]careful what you do, `cause the \[C#]lie becomes the truth, hey
\endverse

\beginchorus
\[F#m]Billie Jean is not my lover,
She's just a girl who claims that I am the \[Bm]one
But the kid is not my \[F#m]son  
She says I am the one, \[Bm]
But the kid is not my \[F#m]son
\endchorus

\beginverse
For forty days and forty nights, law was on her side
But who can stand when she`s in demand,
Her scemes and plans
`Cause we danced on the floor in the round.
So take my strong advice: Just remember to always think twice
\endverse

\beginverse
{\nolyrics Chorus}
\endverse

\beginverse
She told my baby we danced till three, and she looked at me,
Then showed a photo. My baby cried.
His eyes were like mine.
Can we dance on the floor in the round?
\endverse

\beginverse
People always told me, be careful what you do.
And don`t go around breaking young girls' hearts.
But you came and stood right by me, just a smell of sweet perfume.
This happened much too soon. She called me to her room, hey hey
\endverse

\beginverse
{\nolyrics Chorus}
\endverse

\endsong
