

\beginsong{Muppets - The Rainbow Connection}

\gtab{Am}{X02200}
\gtab{Am7}{X02000}
\gtab{Bm7}{X24232}
\gtab{C}{X32010}
\gtab{C7}{X30010}
\gtab{C/D}{X02010}
\gtab{D}{XX0232}
\gtab{D7}{XX0212}
\gtab{E7}{020100}
\gtab{Em}{022000}
\gtab{Em7}{020000}
\gtab{F#m7/A}{X02222}
\gtab{F#m7/B}{X22222}
\gtab{G}{320003}

\beginverse
{\nolyrics Intro: \[G] \[C/G] \[G] \[C/G] }
\endverse

\beginverse
\[G]Why are there \[Em]so many \[Am]songs about \[C/D]rain\[D]bows, 
and \[G]what's on the \[Em]other \[C]side? \[C/D] \[D7]
\[G]Rainbows are \[D/E]vi\[Em7]sions, but \[Am]only \[C/D]illu\[D]sions, 
and \[G]rainbows have \[Em]nothing to \[C7]hide.
\[C7]So, we've been told and some choose to believe it,
\[F#m7/A]I know they're \[F#m7/B]wrong wait and \[F#m7/A]see. \[F#m7/B]
\endverse

\beginchorus
\[Am7]Someday we'll \[D]find \[C/D]it, the \[Bm7]rainbow con\[E7]nection, 
the \[Am]lovers the \[D7]dreamers and \[G]me.
\endchorus

\beginverse
\[G]Who said that \[Em]every \[Am]wish would be \[C/D]heard \[D]and 
\[G]answered when \[Em]wished on \[C]the \[C/D]morning \[D7]star?
\[G]Somebody \[D/E]thought of \[Em7]that, \[Am]and \[C/D]someone be\[D]lieved it, 
\[G]look what its \[Em]done so far. \[C7]
\[C7]What's so amazing that keeps us stargazing, 
and \[F#m7/A]what do we \[F#m7/B]think we might \[F#m7/A]see? \[F#m7/B]
\endverse

\beginverse
[Chorus]
\endverse

\beginverse
\[D/F#]All of us \[Em]under its \[G/D]spell, we \[C]know that its \[G/B]probably \[C/D]mag\[D7]ic.
\endverse

\beginverse
\[G]Have you \[Em]been half \[Am]asleep and \[C/D]have you \[D]heard \[G]voices?  
\[G]I've \[Em]heard \[C]them \[C/D]calling my \[D7]name.
\[G]Is this the \[D/E]sweet \[Em7]sound, \[Am]that calls \[C/D]the young \[D]sailors? The \[G]voice might be one and the \[Em]same.
\endverse

\beginverse
\[C7]I've heard it too many times to ignore it, 
It's \[F#m7/A]something that \[F#m7/B]I'm sup\[F#m7/A]posed to \[F#m7/B]be.
\endverse

\beginverse
[Chorus]
\endverse
\endsong


