

\beginsong{Nixons - Sister}

\gtab{Am}{X02210}
\gtab{C}{X32030}
\gtab{D}{X00232}
\gtab{Em}{022000}
\gtab{G}{320003}

\beginverse
\[G]Here I am \[D]again \[Em]again, overwhelmed with fee\[C]ling. \[Am]
\[G]Thousand miles away\[D] From your \[Em]ocean home. \[C] \[Am]
\[C]Part of me is \[Am]near.
\endverse

\beginverse
\[G]Thoughts of what we \[D]were \[Em]Invade. \[C] \[Am]
\[G]Miles that stand between\[D] Can't \[Em]separate. \[C] \[Am]
You're \[C]all I hoped you'd \[Am]become.
\endverse

\beginchorus
\[G]Sister, I \[D]see you
\[Am]Dancing on the stage \[C]of memory
\[G]Sister, I \[D]miss you.
\endchorus

\beginverse
\[G]Fleeting visits \[D]pass Still they \[Em]satisfy. \[C] \[Am]
\[G]Reminders of the \[D]next Overshadow \[Em]goodbye.  \[C] \[Am]
\[C]Our flames burn as \[Am]one.
\endverse

\beginverse
[Chorus]
\endverse

\beginverse
\[G]All I am \[D]begins with you.
\[Am]Thoughts of hope \[C]understood.
\[G]Half of me \[D]breathes in you.
\[Am]Thoughts of love \[C]remain \[D] true. \[G]
\endverse

\beginverse
\[G]Here we are a\[D]gain saying \[Em]goodbye. \[C] \[Am]
\[G]Still we'll fall a\[D]sleep underneath the \[Em]same sky. \[C] \[Am]
Your \[C]all I knew you'd \[Am]become.
\endverse

\beginverse
[Chorus]
\endverse

\beginverse
Inter\[G]twined you and \[D]I.
Our \[Am]souls speak from \[C]across the \[D]miles.
Inter\[G]twined you and \[D]I.
Our \[Am]blood flows from the \[C]same \[D]in\[G]side.
\endverse

\beginverse
\[G]All I have \[D]begins with you.
\[Am]Thoughts of hope \[C]understood. \[D]
\[G]Half of me \[D]breathes in you.
\[Am]Thoughts of love \[C]remain \[D]true. \[G]
When I, \[C]when I \[D]close my eyes,
\[G]I see you walking there, \[D]
I see you dancing in my \[Am]mind. \[C] \[Em]
\endverse

\endsong


