

\beginsong{Queen - Bohemian Rhapsody }

\gtab{A}{X02220}
\gtab{Ao}{XX1212}
\gtab{A&}{XX6544}
\gtab{A&o}{XX0101}
\gtab{A&m}{XX6444}
\gtab{A&/E&}{XX1114}
\gtab{B}{224442}
\gtab{B&}{113331}
\gtab{B&6}{XX3333}
\gtab{B&7}{113131}
\gtab{B&11}{X11111}
\gtab{B&/D}{XX0331}
\gtab{B+}{XX5443}
\gtab{B&m}{113321}
\gtab{B&m/D&}{X43321}
\gtab{Bm}{X24432}
\gtab{C7}{X32310}
\gtab{C7-9}{X32323}
\gtab{C/G}{332010}
\gtab{Cm}{XX1013}
\gtab{Cm7}{XX1313}
\gtab{C#o}{XX2323}
\gtab{D}{XX0232}
\gtab{D&}{XX3121}
\gtab{D&/A&}{4X3121}
\gtab{D&/C&}{X2X121}
\gtab{E}{022100}
\gtab{E&}{XX1343}
\gtab{E&/B&}{X11343}
\gtab{E&/G&}{XX5343}
\gtab{E&o}{XX1212}
\gtab{F}{XX3211}
\gtab{F7}{131211}
\gtab{F/A}{X03211}
\gtab{Fm/A&}{4X3111}
\gtab{F/C}{X33211}
\gtab{Fm}{XX3111}
\gtab{Fm7}{131111}
\gtab{F#o}{XX4545}
\gtab{G}{320003}
\gtab{G7}{320001}
\gtab{G&}{244322}
\gtab{G&7}{XX4320}
\gtab{Gm}{XX0555}
\gtab{Gm7}{313333}
\gtab{Gm/D}{X55333}

\beginverse
\[B&6]Is this the real life?  \[C7]Is this \[B&6]just \[C7]fantasy?  
\[F7]Caught in a \[Cm7]land\[F7]slide, no es\[B&]cape from \[Cm7]re\[B&]ality.
\[Gm]Open your eyes, look \[B&7]up to the skies and \[E&]see.
\endverse

\beginverse
\[Cm]I'm just a poor boy, \[F7]  I need no sympathy, because I'm 
\[B]easy \[B&]come, \[A]easy \[B&]go, \[B]little \[B&]high, \[A]little \[B&]low.
\[E&]Anyway the \[B&/D]wind blows \[C#o]doesn't really \[F/C]matter to \[F]me, to \[B&]me.
\endverse

\beginverse
\[B&]Mama, just \[Gm]killed a man, put a \[Cm]gun against his head, pulled my trigger, now he's \[F]dead.  
\[B&]Mama, life had \[Gm]just begun, but \[Cm7]now I've gone and 
\[B+]thrown it \[E&/B&]all a\[F/A]way. \[Fm/A&]
\endverse

\beginverse
\[E&]Mama, \[B&/D&]oooooh\[Cm] didn't \[Fm]mean to make you cry.  
If \[B&]I'm not back again this time to\[E&]morrow, carry \[B&/D&]on, carry \[Cm]on
as if \[A&m] nothing really \[E&]matters. \[A&] \[E&] \[E&o] \[Fm7] \[B&]
\endverse

\beginverse
\[B&]Too late, my \[Gm]time has come, sends \[Cm]shivers down my spine, body's \[F]aching all the time.
\[B&]Goodbye, everybody, I've \[Gm]got to go, gotta \[Cm7]leave you all
be\[B+]hind and \[E&/B&]face the \[F/A]truth. \[Fm/A&]
\endverse

\beginverse
\[E&]Mama, \[B&/D&]oooooh\[Cm] I don't \[Fm]want to die,
I \[B&]sometimes wish I'd never been born at \[E&]all.
\endverse

\beginverse
{\nolyrics \[B&/D] \[Cm] \[Fm] \[B&7] \[Eb] \[Gm/D] \[Cm] \[Fm] \[D] \[D&/C&] \[B&m]}
\endverse

\beginverse
\[A] \[D]I \[A]see a \[Ao]little \[A]silhou\[D]etto \[A]of a \[Ao]man.  
\[A]Scara\[D]mouche, \[A]Scara\[D]mouche, \[A]will you \[Ao]do the \[A]Fan\[D]dan\[A]go?
\[D&/A&]Thunderbolt and \[A&]lightning \[C/G&]very, very \[E]frightening \[A]me.
\endverse

\beginverse
Gallileo, Gallileo, Gallileo, Figaro, Magnifico.
\endverse

\beginverse
\[B]I'm \[B&]just a \[A]poor \[B&]boy, \[B]no\[B&]body \[A]loves \[B&]me.  
\[A&]He's \[E&]just a \[E&o]poor \[E&]boy \[A&]from a \[E&]poor \[E&o]fami\[E&]ly.
\[A&]Spare him his \[E&/G]life from this \[F]monstrosi\[B&]ty.
\endverse

\beginverse
{\nolyrics \[A&] \[E&/G] \[F#o] \[Fm7]}
\endverse

\beginverse
\[B]Easy \[B&]come, \[A]easy \[B&]go, \[B]will you \[B&]let me \[A]go?  \[B&]Bis\[E&]millah!
No, \[B&]we will not let you go.  \[E&]Bismillah!
\[B&]We will not let you go.  \[E&]Bismillah!  \[B&]We will not let you go.
\endverse

\beginverse
Will not let you go.  Will not let you go. \[G&7]Ahhhhhhhhh
\[Bm]No, \[A]no, \[D]no, \[D&]no, \[G&]no, \[B&]no, \[E&]no.
\[E&]Mama mia, let me \[B&]go.  Be\[E&]elze\[A&]bub has a \[D]devil put a\[Gm]side for \[B&]me,for me, for me! \[E&] \[F7]
\endverse

\beginverse
\[B&7] So you \[E&/B&]think you can \[B&]stone me and \[E&]spit in my \[B&]eye? \[D&]
\[B&7] So you \[E&/B&]think you can \[B&]love me and \[E&]leave me to \[A&]die?
\endverse

\beginverse
\[Fm]Oh, \[B&]baby, \[Fm7]can't do this to me, \[B&]baby.
\[Fm7]Just gotta get \[B&]out, \[Fm7]just gotta get \[B&]right outta' \[E&]here. \[B&7]
\endverse

\beginverse
\[E&] \[B&/D] \[Cm] \[G] \[Cm] \[G7] \[Cm] \[Bb7] \[Eb] \[D] \[Gm] \[Ab] \[Eb]
\[Cm]Nothing really \[Gm]matters, \[Cm]anyone can \[Gm]see.
\[Cm]Nothing really \[A&m]matters, \[B&11]nothing really matters to \[E&]me. \[A&/E&]
\endverse

\beginverse
\[E&] \[E&o] \[B&/D] \[B&m/D&] \[C7] \[C7-9] \[C7] \[F]
\[B&]Any\[F]way the \[A&o]wind \[Gm7]blows. \[F]
\endverse

\endsong
