

\beginsong{R.E.M. - It’s the End of the World as We Know It}

\gtab{Am}{X02220}
\gtab{B&}{113331}
\gtab{C7}{032030}
\gtab{Dsus2}{XX0230}
\gtab{G}{320003}

\beginverse
\[G]That's great, it starts with an \[C7]earthquake,
birds and snakes, an \[G]aeroplane - Lenny Bruce is \[C7]not afraid.
\[G]Eye of a hurricane, listen to yourself churn \[C7]world serves its own needs, don't misserve your own needs.
\[G]Feed it up a knock, speed, grunt no, strength no. \[C7]Ladder structure clatter with fear of height, down height.
\[B&]Wire in a fire, represent the seven games in a \[Am]government for hire and a combat site.
\endverse
 
\beginverse 
\[G]Left her, wasn't coming in a hurry with the furies breathing \[C7]down your neck.
\[G]Team by team reporters baffled, trump, tethered crop. Look at that \[C7]low plane!  Fine then.
\[G]Uh oh, overflow, population, common group, but \[C7]it'll do. Save yourself, serve yourself.
World serves its \[G]own needs, listen to your heart bleed. Tell me with the \[C7]rapture and the reverent in the right - right.
You \[B&]vitriolic, patriotic, slam, fight, bright light, \[Am]feeling pretty psyched.
\endverse
 
\beginchorus
It's the \[G]end of the \[Dsus2]world as we \[Am]know it
It's the \[G]end of the \[Dsus2]world as we \[Am]know it
It's the \[G]end of the \[Dsus2]world as we \[Am]know it and I feel \[C]fine
\endchorus
 
\beginverse
\[G]Six o'clock - TV hour.  Don't get caught in foreign tower. \[C7]Slash and burn, return, listen to yourself churn.
\[G]Lock him in uniform and book burning, blood letting. \[C7]Every motive escalate.  Automotive incinerate.
\[G]Light a candle, light a motive.  Step down, step down. \[C7]Watch a heel crush, crush. Uh oh, this means 
\[G]no fear - cavalier.  Renegade and steer clear! A \[C7]tournament, a tournament, a tournament of lies.
\[B&]Offer me solutions, offer me alternatives and \[Am]I decline.
\endverse 
 
\beginverse
[Chorus x2]
\endverse
 
\beginverse
\[G]The other night I tripped a nice continental drift divide.
\[C7]Mount St. Edelite.  Leonard Bernstein.
\[G]Leonid Breshnev, Lenny Bruce and Lester Bangs.
\[C7]Birthday party, cheesecake, jelly bean, boom!
You \[B&]symbiotic, patriotic, slam, but neck, \[Am]right?  Right.
\endverse

\beginverse
[Chorus x3]
\endverse

\endsong
