

\beginsong{R.E.M. - Losing My Religion}

\gtab{Am}{x02210}
\gtab{Am/B}{x2x210}
\gtab{Am/C}{x3x210}
\gtab{Am/D}{xx0210}
\gtab{C}{x32010}
\gtab{D}{xx0232}
\gtab{Dm}{xx0231}
\gtab{Em}{022000}
\gtab{F}{133211}
\gtab{G}{320003}

\beginverse
{\nolyrics \[F] \[Dm] \[G] \[Am] \[Am/B] \[Am/C] \[Am/D] \[Am]}
\endverse

\beginverse
\[G] Oh, \[Am]life is bigger
\[Em] It's bigger than you
And you are \[Am]not me.
The lengths that I will \[Em]go to,
The distance in your \[Am]eyes,
\[Em] Oh no, I've said too \[Dm]much,
I set it \[G]up.
\endverse

\beginchorus
That's me in the \[Am]corner,
That's me in the \[Em]spotlight
Losing my \[Am]religion.
Trying to \[Em]keep up with you.
And I \[Am]don't know if I can do it.
\[Em]Oh no, I've said too \[Dm]much,
I haven't said \[G]enough.
\endchorus

\beginverse
I \[G]thought that I heard you \[F]laughing,
I \[Dm]thought that I \[G] heard you \[Am]sing.
I \[F]think I thought I \[Dm]saw    \[G]you \[Am]try.
\endverse

\beginverse
\[G]Every \[Am]Whisper of every waking \[Em]hour
I'm choosing my con\[Am]fessions,
Trying to \[Em]keep an eye of you
Like a \[Am]hurt lost and blinded fool, fool
\[Em]Oh no, I've said too \[Dm]much,
I set it \[G]up.
\endverse

\beginverse
Consider \[Am]this, consider this,
The \[Em]hint of a century,
Consider \[Am]this: the slip
That \[Em]brought me to my knees failed.
\[Am]What if all these fantasies
Come \[Em]flailing around?
Now I've \[Dm]said too \[G]much.
\endverse

\beginverse
I \[G]thought that I heard you \[F]laughing,
I \[Dm]thought that I \[G] heard you \[Am]sing.
I \[F]think I thought I \[Dm]saw \[G]you \[Am]try.
\endverse

\beginverse
[Chorus]
\endverse

\beginverse
I \[G]thought that I heard you \[F]laughing,
I \[Dm]thought that I \[G] heard you \[Am]sing.
I \[F]think I thought I \[Dm]saw \[G]you \[Am]try.
\endverse

\endsong
