\beginsong{Barefoot Truth - I Prefer}

\gtab{E}{022100}
\gtab{D}{XX0232}
\gtab{A}{002220}
\gtab{B}{224442}
\gtab{C#m}{446654}

\beginverse
\[E]I prefer walk\[D]ing rather \[A]than
running down \[A]the street,
\[E]I prefer smi\[D]ling rather \[A]than frowning
at the people I \[A]might meet
If it were \[E]up to you would you \[D]
look at it \[A]the same? \[A]The same way that I do
Don’t say you’d close your \[E]eyes,
And have no voice of opinion \[D]
\[A]of what \[A]lies before you? I’d say shame on you
\endverse

\beginverse
Cause I \[E]say wo\[D]ah some\[A]thing's gotta give
\[A]I need a simpler life to live,
\[E]Wo\[D]ah look into yourself
\[A]You best \[A]find a better way to measure wealth
\endverse

\beginchorus
\[E]Cause it's\[B] a simple \[D]life for a simple \[A]race,
\[E]beneath \[B]the stars \[D]is where we find our \[A]place
\[E]It's a si\[B]mple love \[D]I'm gonna spread your \[A]way
\[E]it's a si\[B]mple life \[D]just living it day to \[A]day.
\endchorus

\beginverse
\[E]I prefer \[D]climbing rather than \[A]falling from a \[A]tree
\[E]I prefer \[D]singing rather than \[A]whispering \[A]silently
\[E]If it were up to \[D]you would you \[A]look at it the same?
The same way that I \[A]do
Don’t say you’d \[E]close your eyes,
And \[D]have no voice of opinion
\[A]of what \[A]lies before you? I’d say shame on you
\endverse

\beginverse
{\nolyrics [Chorus]}
{\nolyrics [Harmonica solo] \[C#m] \[C#m] \[B] \[A]}
\endverse

\beginverse
I \[E]prefer \[D]helping \[A]rather than \[A]acting helplessly
I \[E]prefer \[D]living \[A]ain't that the \[A]way it's supposed to be?
\[E]If it were up to \[D]you would you \[A]look at it the same?
The same way that I \[A]do
Don’t say you’d \[E]close your eyes,
And have no voice of \[D]opinion
\[A]of what lies before you? I’d say shame on you
\endverse

\beginverse
{\nolyrics [Chorus]}
\endverse

\beginverse
\[E]It's a simple life\[B] I'm gonna\[D] spread around, \[A]
\[E]it's a feeling of \[B]elation you \[D]could get me down \[A]
\[E]It's a simple world\[B] gonna \[D]make a stand \[A]
\[E]it's a \[B]simple life
\[D]just \[A]living it the best we can
\endverse

\endsong