\beginsong{Death Cab for Cutie - I Will Follow You In to the Dark}

\gtab{Am}{X02210}
\gtab{Am/E}{002210}
\gtab{C}{X32010}
\gtab{C/G}{332010}
\gtab{Em}{022000}
\gtab{F}{133211}
\gtab{Fm}{133111}
\gtab{G}{320003}
\gtab{G/B}{12003}

\beginverse
{\nolyrics Intro: \[Am] \[C] \[F] \[C] \[G/B]}
{\nolyrics \[Am] \[C] \[G]}
{\nolyrics \[Am] \[C] \[E] \[Am] \[G] \[F] \[Fm] \[C/G]}
\endverse

\beginverse
\[C/G]Love of mine
someday \[Am/E]you will die,
but I'll be \[F]close behind;
I'll follow \[C]you into the d\[G]ark.
No \[C/G]blinding light
or tunnels to \[Am/E]gates of white,
just our hands \[F]clasped so tight
waiting \[C]for the hint of a \[G]spark. 
\endverse

\beginchorus
If he\[Am]aven and hell de\[C]cide that they \[F]both are satis\[C]fied, \[G/B]
il\[Am]luminate the \[C]noes on their \[G]vacancy signs.
If th\[Am]ere's no one be\[C]side you when your \[Em]soul em\[Am]barks \[G]
then \[F]I'll follow \[Fm]you into the \[C/G]dark.
\endchorus

\beginverse
In \[C/G]Catholic school,
as vicious as \[Am/E]Roman rule,
I got my k\[F]nuckles bruised 
by a \[C]lady in b\[G]lack.
And I \[C/G]held my tongue 
as she \[Am/E]told me "Son, 
fear is the \[F]heart of love".
So I \[C]never went \[G]back.
\endverse

\beginverse
[Chorus]
\endverse
     
\beginchorus
If he\[Am]aven and hell de\[C]cide that they b\[F]oth are satis\[C]fied, \[G/B]
il\[Am]luminate the \[C]noes on their \[G]vacancy signs.
If th\[Am]ere's no one be\[C]side you when your \[E]soul em\[Am]barks \[G]
then \[F]I'll follow \[Fm]you into the \[C/G]dark.
\endchorus

\beginverse
\[C/G]You and me
have seen every\[Am/E]thing to see
from Bangkok to \[F]Calgary, 
and the \[C]soles of your \[G]shoes
are \[C/G]all worn down.
The time for \[Am/E]sleep is now
but it's nothing to \[F]cry about  
'cause we'll \[C]hold each other \[G]soon
in the \[Am]blackest of \[F]rooms.
\endverse

\beginverse
[Chorus]
\endverse
\endsong