

\beginsong{Edward Sharpe and the Magnetic Zeros - Home}

\gtab{Bm}{X24432}
\gtab{D}{XX0232}
\gtab{D/F#}{200232}
\gtab{G}{320003}

\beginverse
{\nolyrics \[Bm] \[D] \[D/F#] \[D] \[G] (x2)}
\endverse

\beginverse
\[Bm]Alabama, Arkansas,
\[D]I do love my ma and pa,
\[D/F#]Not the way that \[D]I do love \[G]you.
\endverse

\beginverse
Well, \[Bm]Holy, Moley, me, oh my,
\[D]You're the apple of my eye,
\[D/F#]Girl I've never \[D]loved one like \[G]you.
\endverse

\beginverse
\[Bm]Man oh man you're my best friend,
\[D]I scream it to the nothingness,
\[D/F#]There ain't \[D]nothing that I \[G]need.
\endverse

\beginverse
\[Bm]Well, hot and heavy, pumpkin pie,
\[D]Chocolate candy, Jesus Christ,
\[D/F#]Ain't nothing \[D]please me more than \[G]you.
\endverse

\beginverse
Ahh \[Bm]Home. Let me come \[D]home
\[D/F#]Home is wher\[D]ever I'm with \[G]you.
Ahh \[Bm]Home. Let me go ho\[D]me.
\[D/F#]Home is wher\[D]ever I'm with \[G]you.
\endverse

\beginverse
{\nolyrics \[Bm] \[D] \[D/F#] \[D] \[G] (x2)}
\endverse

\beginverse
\[Bm]I'll follow you into the park,
\[D]Through the jungle through the dark,
\[D/F#]Girl I never \[D]loved one like \[G]you.
\endverse

\beginverse
\[Bm]Moats and boats and waterfalls,
\[D]Alley-ways and pay phone calls,
\[D/F#]I've been \[D]everywhere with \[G]you.
\endverse

\beginverse
\[Bm]We laugh until we think we’ll die,
\[D]Barefoot on a summer night
\[D/F#]Nothin’ new is \[D]sweeter than with \[G]you
\endverse

\beginverse
\[Bm]And in the streets you run afree,
\[D]Like it's only you and me,
\[D/F#]Geeze, you're \[D]something to \[G]see.
\endverse

\beginverse
Ahh \[Bm]Home. Let me come \[D]home
\[D/F#]Home is wher\[D]ever I'm with \[G]you.
Ahh \[Bm]Home. Let me go ho\[D]me.
\[D/F#]Home is wher\[D]ever I'm with \[G]you.
\endverse

\beginverse
\[Bm]Home. Let me come \[D]home.
\[D/F#]Home is wher\[D]ever I'm with \[G]you.
\[Bm]Ahh home. Yes I am h\[D]ome.
\[D]Home is when I'm alone with \[G]you.
\endverse

\beginverse
\[Bm]Alabama, Arkan\[D]sas,
\[D/F#]I do love my \[D]ma and \[G]pa
\[Bm]Moats and boats and water\[D]falls,
\[D/F#]Alley-ways and \[D]pay phone \[G]calls
\endverse

\beginverse
\[Bm]Home...   \[D]Home...
\[D/F#]Home is when \[D]I'm alone with \[G]you.
\[Bm]Home...   \[D]Home...
\[D/F#]Home is when \[D]I'm alone with \[G]you...
\endverse

\endsong
