

\beginsong{R.E.M. - Half a World Away}

\gtab{Am}{X02220}
\gtab{D}{XX0232}
\gtab{Em}{022100}
\gtab{F}{133211}
\gtab{G}{320003}

\beginverse
{\nolyrics Intro: \[Am] \[G] \[D] \[Em]}
\endverse

\beginverse
\[Am]This could be the \[G]saddest dusk I've \[D]ever seen \[Em]
turn to a \[Am]miracle, \[G]high ali\[D]ve. \[Em]
My mind is \[Em]racing, \[G]as it alw\[D]ays will. \[Em]
My hands tired, my \[Am]heart aches.
I'm \[G]half a world aw\[D]ay here, my \[Em]head sworn to \[F]go it alone,
and \[F]hold it along, \[D]haul it along and hold it.
\[F]Go it alone, and hold it along. \[D]Ohhhhhh
\endverse

\beginverse
\[D]Oh \[G]lonely deep sit \[D]hollow.
\[Em]Half a world, \[Am]half a world a\[G]way.
My \[D]shoes are gone, my \[Em]life spent. \[Am]
I've \[G]had too much to \[D]drink.
I \[Em]didn't think, I \[Am]didn't think of \[G]you.
I \[D]guess that's all I \[Em]need-ed.
To \[F]go it alone, and \[F]hold it along, \[D]haul it along, and hold it.
\[F]Backwards, blackbirds, forwards and fall.
\endverse

\beginverse
\[D]Oh \[G]lonely world is \[D]wasted.
\[Em]Pathetic eyes, \[Am]high alive. \[G]
\[D]Blind to the tide \[Em]that turns the sea. \[Am]
This \[G]storm it came up strong. \[D]
It s\[Em]hook the trees and \[Am]blew away our \[G]fear.
I \[D]couldn't even \[Em]hear.
\endverse

\beginverse
To \[F]go it alone, and \[F]hold it along, \[D]haul it along, and hold it.
\[F]Go it alone, and \[F]hold it along. \[D]Ohhhhhhhh
\[F]Go it alone, and \[F]hold it along, \[D]haul it along, and hold it.
\[F]Blackbirds, backwards, forwards and fall. And \[D]ohhhhhh
\endverse

\beginverse
Oh and \[G]this could be the \[D]saddest dusk
I \[Em]ever seen \[Am]turn to a \[G]miracle, \[D] high \[Em] alive.
\[Am]My mind is \[G]racing, \[D] as it \[Em]always will.
My \[Am]hands tired, my \[G]heart aches.
I'm \[D]half a world \[Em]away.
\endverse

\beginverse
And \[Am]Ohhh\[D]hhh\[G]hh.
\endverse

\endsong
