

\beginsong{Simon and Garfunkel - Sound of Silence}

\gtab{C}{032010}
\gtab{C/G}{332010}
\gtab{D}{XX0232}
\gtab{Em}{022000}
\gtab{G}{320003}

\beginverse
\[Em]   Hello darkness, my old \[D]friend,
I've come to talk with you \[Em]again,
Because a vision \[C]softly cree\[G]ping,
Left it's \[Em]seeds while I w\[C]as slee\[G]ping,
And the \[C]vision that was pl\[C/G]anted in my \[G]brain
Still \[Em]remains
Within the so\[D]und of \[Em]silence.
\endverse

\beginverse
\[Em]In restless dreams I walked a\[D]lone
Narrow streets of cobble\[Em]stone,
'\[Em]Neath the halo of \[A]a street \[G]lamp,
I turned my \[Em]collar to the \[C]cold and \[G]damp
When my \[C]eyes were stabbed by the flash of a neon\[G]light
That split the \[Em]night
And touched the \[D]sound of \[Em]silence.
\endverse

\beginverse
\[Em]  And in the naked light I \[D]saw
Ten thousand people, maybe \[Em]more.
\[Em]People talking wit\[C]hout spea\[G]king,
\[Em]People hearing with\[C]out liste\[G]ning,
People writing so\[C]ngs that voices never \[G]share
And no one \[Em]dare
Disturb the \[D]sound of \[Em]silence.
\endverse

\beginverse
\[Em] Fools said i, you do not \[D]know
Silence like a cancer \[Em]grows.
\[Em]Hear my words that I \[C]might teach \[G]you,
\[Em]Take my arms that I \[C]might reach \[G]you.
But my wo\[C]rds like silent raindrops \[G]fell,
And \[Em]echoed
In the \[D]wells of \[Em]silence
\endverse

\beginverse
\[Em] And the people bowed and \[D]prayed
To the neon God they \[Em]made.
\[Em] And the sign flashed out \[C]it's war\[G]ning,
\[Em]In the words that it \[C]was \[G]forming.
And the \[Em]sign said, the \[C]words of the prophets
Are \[C]written on the subway \[G]walls
And tenement \[Em]halls.
And whispered in the \[D]sounds of \[Em]silence.
\endverse

\endsong
