\beginsong{Talking Heads - Once in a Lifetime}

\gtab{A}{X02220}
\gtab{D}{XX0232}
\gtab{D/F#}{2XX232}
\gtab{D/A}{X0X232}
\gtab{F#m}{244222}
\gtab{G}{320003}

\beginverse
{\nolyrics Intro: (\[F#m]-\[A] \[A]-\[F#m]) x4 \[F#m]-\[A]}
\endverse

\beginverse
\[A]And you may find yourself, \[F#m]living in a shotgun shack
\[A]And you may find yourself, \[F#m]in another part of the world
\[A]And you may find yourself, \[F#m]behind the wheel of a large automobile
\[A]And you may find yourself, in a beautiful \[F#m]house, with a \[A]beautiful wife \[F#m]
And you may \[F#m]ask yourself, \[A]well, how did I \[F#m]get \[A]here? 
\endverse

\beginchorus
\[A]Letting the \[D]days go by, \[F#]let the \[G]water hold me down
\[A]Letting the \[D]days go by, \[F#]water \[G]flowing underground
\[A]Into the \[D]blue again, \[F#]after the \[G]money's gone
\[A]Once in a \[D]lifetime, \[F#]water \[G]flowing underground
\endchorus

\beginverse
\[A]And you may ask yourself, \[F#m]how do I work this? 
\[A]And you may ask yourself, \[F#m]where is that large automobile? 
\[A]And you may tell yourself, \[F#m]this is not my beautiful house 
\[A]And you may tell yourself, \[F#m]this is not my beautiful wife 
\endverse

\beginverse
[Chorus]
\endverse

\beginverse
\[A]Same as it ever was, same as it ever was, \[F#]same as it ever was, same as it ever was,
\[A]same as it ever was, same as it ever was, \[F#]same as it ever was, same as it ever was, 
\[A]Water dissolving, and water removing, \[F#]there is water at the bottom of the ocean
\[A]Carry the water at the bottom of the ocean, \[F#]remove the water at the bottom of the ocean!
\endverse

\beginverse
[Chorus]
\endverse

\beginverse
\[A]And you may ask yourself, \[F#]what is that beautiful house? 
\[A]And you may ask yourself, \[F#]where does that highway go to? 
\[A]And you may ask yourself, \[F#]am I right? am I wrong? 
\[A]And you may tell yourself, \[F#]My God, what have I done? 
\endverse

\beginverse
\[A]Letting the \[D]days go by, \[F#]let the \[G]water hold me down
\[A]Letting the \[D]days go by, \[F#]water \[G]flowing underground
\[A]Into the \[D]blue again, \[F#]in the \[G]silent water
\[A]Under the \[D]rocks and stones, \[F#]there is \[G]water underground
\[A]letting the \[D]days go by, \[F#]let the \[G]water hold me down
\[A]Letting the \[D]days go by, \[F#]water \[G]flowing underground
\[A]Into the blue \[D]again, \[F#]after the \[G]money's gone
\[A]Once in a \[D]lifetime, water \[F#]flowing \[G]underground
\endverse

\beginverse
\[D]Same as it ever was, \[C]same as it \[G]ever was, 
\[D]same as it ever \[C]was, \[G]look where my hand \[D]was
Time isn't holding \[C]up, \[G]time isn't after us, 
\[D]same as it ever was\[C], \[G]same as it ever \[D]was
Same as it ever was, \[C]same as it \[G]ever was, 
\[D]same as it ever was, \[C]same as it \[G]ever was \[D]
After the rain holds up, \[C]same as it \[G]ever was\[D], 
then a twister comes, \[C]here comes the \[G]twister \[D]
Same as it ever was, \[C]same as it \[G]ever was \[D]
\endverse

\endsong