

\beginsong{The Decemberists - The Legionnaire's Lament}

\gtab{A}{X02220}
\gtab{B&}{X13331}
\gtab{B&m}{X13321}
\gtab{C}{032010}
\gtab{Dm}{XX0232}
\gtab{F}{133211}
\gtab{G}{320003}
\gtab{Gm}{3:022100}

\beginverse
I'm a \[Dm]legionnaire, camel in \[F]disrepair,
Hoping for a \[G]Frigidaire to come \[B&]passing by.\[A]
I am \[Dm]on reprieve, lacking my \[F]joie de vivre,
Missing my \[G]gay Pari in this \[B&]desert \[A]dry.
\endverse

\beginverse
And I \[Dm]wrote my girl, told her I \[F]would not return,
I've terribly \[G]taken a turn for the \[B&]worse now, I \[A]fear.  
It's been a \[Dm]year or more
Since they shipped me to this \[F]foreign shore, 
Fighting in a \[G]foreign war, 
So far away\[B&] from my \[A]home.
\endverse

\beginchorus
If only some \[F]rain would fall on the \[C]houses and the boulevards 
And the \[Gm]sidewalk bagatelles (it's like a \[B&]dream).
With a r\[F]oar of cars and the \[C]lolling of the cafe bars 
The \[Gm]weetly sleeping sweeping of the \[B&]Seine.
Lord, I \[B&m]don't know if I'll ever be back again.\[Dm]
La Da \[F]Dum Dum La Da \[G]Da Dum \[B&] \[A]
\endchorus

\beginverse
Medicating \[Dm]in the sun with pinch doses of \[F]laudanum, 
Longing for the \[G]old fecundity \[B&]of my home\[A]land.  
Curses \[Dm]to this mirage!  A bottle of \[F]ancient Shiraz!  
The smattering of \[G]distant applause is ringing \[B&]in my poor \[A]ears. 
On the \[Dm]old left bank, my baby in a \[F]charabanc, 
Riding up the \[G]width and length of the \[B&]Champs Ely\[A]see.
\endverse

\beginverse
[Chorus]
\endverse

\endsong
