\beginsong{The Band - The Weight}

\gtab{A}{002220}
\gtab{C#m}{X46654}
\gtab{D}{XX0232}
\gtab{A/G#}{402224}
\gtab{F#m7}{202220}
\gtab{E}{022100}

\beginverse
\[A]I pulled in to \[C#m]Nazareth, I was 
\[D]feeling about half past \[A]dead.
\[A]I just need some \[C#m]place where 
\[D]I can lay my \[A]head.
\[A]``Hey, Mister, can you \[C#m]tell me where a 
\[D]man might find a \[A]bed?''
\[A]He just grinned, \[C#m]shook my hand, 
\[D]``No'' was all he \[A]said.
\endverse

\beginchorus
\[A]Take a \[A/G#]load off, \[D]Fanny.
\[A]Take a \[A/G#]load for \[D]free.
\[A]Take a \[A/G#]load off, \[D]Fanny.
\[D]And...  you put the load right on \[A]me.
\endchorus

\beginverse
{\nolyrics [Instrumental] \[A/G#] \[F#m7] \[E] \[D] }    
\endverse

\beginverse
\[A]I picked up my \[C#m]bag.  I went 
\[D]looking for a place to hide. \[A]
\[A]When I saw Carmen \[C#m]and the 
\[D]devil walking si\[A]de by side.
\[A]I said, ``Hey, Carmen, \[C#m]come on.  
\[D]Let'sgo downtown.'' \[A]
\[A]She said, ``I got \[C#m]to go, but my 
\[D]friend can stick \[A]around.''
\endverse

\beginverse
{\nolyrics [Chorus] }    
\endverse

\beginverse
\[A]Go down, Miss Moses, \[C#m]there's 
\[D]nothing you can \[A]say.
\[A]It's just old Luke, \[C#m]and Luke's 
\[D]waiting on \[A]the judgement day.
\[A]``Well, Luke, my \[C#m]friend, what 
\[D]about young \[A]Anna Lee?''
\[A]He said, ``Do me a \[C#m]favor, son, 
\[D]won't you stay and \[A]keep Anna Lee company.''
\endverse

\beginverse
{\nolyrics [Chorus] }    
\endverse

\beginverse
\[A]Crazy Chester follow\[C#m]ed me and he 
\[D]caught me in the \[A]fog.
\[A]He said, ``I will fix \[C#m]your rack, 
\[D]if you'll take Jack\[A]my dog.''
\[A]I said, ``Wait a min\[C#m]ute, Chester. 
\[D]You know I'm a \[A]peaceful man.''
\[A]He said, ``That's \[C#m]okay, boy.  
\[D]Won't you feed him \[A]when you can?''
\endverse

\beginverse
{\nolyrics [Chorus] }    
\endverse

\beginverse
\[A]Get your Canonball \[C#m]now, 
to take me \[D]down the line. \[A]
\[A]My bag is sinking low\[C#m], 
and I do be\[D]lieve it's time \[A]
\[A]To get back to Miss \[C#m]Fanny.  
You kn\[D]ow she's the only \[A]one
\[A]Who sent me here with\[C#m] 
her regards \[D]for everyone. \[A]
\endverse

\beginverse
{\nolyrics [Chorus] }    
\endverse

\endsong