\beginsong{The Beatles - With A Little Help From My Friends}

\gtab{G}{320001}
\gtab{D}{XX0232}
\gtab{A}{002220}
\gtab{E}{022100}
\gtab{Bm}{224432}
\gtab{E7}{020100}
\gtab{F#m}{244222}

\beginverse
{\nolyrics [Intro] \[G] \[D] \[A] x5}
\endverse

\beginverse
\[A]What would you \[E]do if I \[Bm]sang out of tune,  
would you \[E]stand up and \[E7]walk out on \[A]me? 
Lend me your \[E]ears and I'll \[Bm]sing you a song  
and I'll \[E]try not to \[E7]sing out of \[A]key. 
\endverse

\beginchorus
\[A]Oh, I'm gonna get \[G]by with a little \[D]help from my \[A]friends. 
I just keep trying, \[G]high with a little \[D]help from my \[A]friends. 
I wanna get high, \[G]high with a little \[D]help from my \[A]friends. 
I just hold \[G]on \[D]with my \[A]friends. 
\endchorus
  
\beginverse
\[A]What do I \[E]do when my \[Bm]love is away? 
Does it \[E]worry you to \[E7]be a\[A]lone? Oh no! 
How do I \[E]feel by the \[Bm]end of the day ? 
Are you \[E]sad because you're \[E7]on your \[A]own? 
(I don't get sad!) 
\endverse

\beginverse
[Chorus]
\endverse

\beginverse
\[A]Do you need any\[F#m]body?...I \[A]need some\[G]body to \[A]love. 
Could it be any\[F#m]body? All I need is \[E]someone, 
\[E7]Lord, I need someone...\[G]I want some\[D]body to \[A]love.
\endverse

\beginverse
[Chorus]
\endverse

\beginverse
\[A]Would you be\[E]lieve in a \[Bm]love at first sight? 
I'm \[E]certain that it \[E7]happens all the \[A]time. 
What \[E]do you see when you \[Bm]turn out the light? 
I don't \[E]see too much, but I \[E7]know it's \[A]mine. 
\endverse

\beginverse
[Chorus]
\endverse

\beginverse
\[A]Do you need any\[F#m]body?...\[A]I need some\[G]body to \[A]love.
Could it be any\[F#m]body? All I need is \[E]someone, 
\[E7]Lord, I need someone...\[G]I want some\[D]body to \[A]love. 
\endverse

\beginverse
[Chorus x2]
\endverse

\endsong